Using simulation to optimize the sampling design of fisheries-independent trawl surveys

### 2018-07-04 analysis/paper/sim_survey_paper.Rmd
Describe cohort model

>>>>

# Methods

The simulation presented here starts with a common cohort model where the abundance at age $a$ in year $y$ ($N_{a,y}$) equals the abundance of that cohort in the previous year multiplied by the survival rate, which is expressed in terms of total mortality ($Z_{a,y}$):
$$N_{a,y} = N_{a-1,y-1} e^{-Z_{a-1,y-1}}$$
Here, numbers-at-age in the first year are filled via exponential decay, $N_{a,1} = N_{a-1,1} e^{-Z_{a-1,1}}$, numbers at age 1 (i.e. recruits) are filled using a random walk, $log(N_{1,y}) = log(N_{1,y-1}) + \epsilon_{y-1}$, and total mortality is set to a baseline level plus process error, $log(Z_{a,y}) = log(z) + \delta_{a,y}$. The error around the recruitment process was simulated using the normal distribution, $\epsilon_{y} \sim N(0, \sigma_{r}^{2})$, and the process error was simulated using the covariance structure described in Cadigan [-@Cadigan2016]
$$\begin{eqnarray}
Cov(\delta_{a,y}, \delta_{a-i,y-j}) &=& \frac{\sigma_{\delta}^2 \varphi_{\delta, age}^i \varphi_{\delta, year}^j}{(1 - \varphi_{\delta, age}^2)(1 - \varphi_{\delta, year}^2)} \\
Corr(\delta_{a,y}, \delta_{a-i,y-j}) &=& \varphi_{\delta, age}^i \varphi_{\delta, year}^j
\end{eqnarray}
$$

This structure allows for autocorrelation in process errors over ages and years (i.e. total mortality can be made to be more similar for fish that are closer together in age and time). Overall, this  formulation allows for the simulation of an array of population dynamics that one might expect to observe.
